cardinalR: Generating Interesting High-Dimensional Data Structures

### 2025-12-12 paper-cardinalR.Rmd
Added table caption for the argument table

```{r}
arg_branching_tb <- tibble(arg = c("n", "k", "p", "h", "ratio", "s", "r", "k", "loc", "w", "steps", "spins", "hc", "non_fac"), 
                          type = c("integer", "integer", "integer", "",
                                   "", "", "", "", "", "", "", "", "", ""),
                        exp = c("Number of points.",
                                "Number of clusters.",
                                "Number of dimensions.",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "")) |> 
   mutate(arg = gsub("_", "\\\\_", arg))
```

```{r arg-shape-tb-html, eval=knitr::is_html_output()}
arg_branching_tb |> 
  mutate(arg = paste0("<code>", arg, "</code>")) |>
  kable(caption = "The main arguments for branching shape generators.", col.names = c("Argument", "Type", "Explanation"), escape = FALSE, table.pos = "!ht") 
```

```{r arg-shape-tb-pdf, eval=knitr::is_latex_output()}
arg_branching_tb |> 
  mutate(arg = paste0("\\texttt{", arg, "}")) |> 
  kable(caption = "The main arguments for branching shape generators.", format="latex", col.names = c("Argument", "Type", "Explanation"), booktabs = T, escape = FALSE, table.pos = "!ht")  |>
  column_spec(1, width = "1cm") |>
  column_spec(1, width = "2cm") |>
  column_spec(2, width = "3cm")
```

>>>>

```{r}
arg_branching_tb <- tibble(arg = c("n", "k", "p", "h", "ratio", "s", "r", "k_small", "r_vec", "spe", "w", "steps", "spins", "hc", "non_fac"), 
                          type = c("integer", "integer", "integer", "real value",
                                   "real value", "real value", "real value", "integer", "real values", "real value", "real value", "integer", "integer", "real value", "real value"),
                        exp = c("Number of points.",
                                "Number of clusters.",
                                "Number of dimensions.",
                                "Height.",
                                "Radius tip to radius base ratio.",
                                "Variance-covariance matrix.",
                                "Radius.",
                                "Number of small spheres.",
                                "Radius of the big and small spheres.",
                                "How far the small spheres are placed from each other.",
                                "Vertical variation",
                                "Number of steps for the theta parameter.",
                                "Number of loops of the spiral.",
                                "Steepness and vertical scaling of the hyperbola.",
                                "Strength of this sinusoidal effect.")) |> 
   mutate(arg = gsub("_", "\\\\_", arg))
```

```{r arg-shape-tb-html, eval=knitr::is_html_output()}
arg_branching_tb |> 
  mutate(arg = paste0("<code>", arg, "</code>")) |>
  kable(caption = "Argument definitions for the shape generators. The table lists each argument, its data type, and a description of its role in controlling geometric structure, dimensionality, scaling, curvature, spacing, and other features of the simulated high-dimensional datasets.", col.names = c("Argument", "Type (positive)", "Explanation"), escape = FALSE, table.pos = "!ht") 
```

```{r arg-shape-tb-pdf, eval=knitr::is_latex_output()}
arg_branching_tb |> 
  mutate(arg = paste0("\\texttt{", arg, "}")) |> 
  kable(caption = "Argument definitions for the shape generators. The table lists each argument, its data type, and a description of its role in controlling geometric structure, dimensionality, scaling, curvature, spacing, and other features of the simulated high-dimensional datasets.", format="latex", col.names = c("Argument", "Type (positive)", "Explanation"), booktabs = T, escape = FALSE, table.pos = "!ht")  |>
  column_spec(1, width = "1cm") |>
  column_spec(1, width = "2cm") |>
  column_spec(2, width = "3cm")
```

### 2025-12-12 paper-cardinalR.tex
Added table caption for the argument table

\caption{\label{tab:arg-shape-tb-pdf}The main arguments for branching shape generators.}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{3cm}l}
\toprule
Argument & Type & Explanation\\
\midrule
\texttt{n} & integer & Number of points.\\
\texttt{k} & integer & Number of clusters.\\
\texttt{p} & integer & Number of dimensions.\\
\texttt{h} &  & \\
\texttt{ratio} &  & \\
\addlinespace
\texttt{s} &  & \\
\texttt{r} &  & \\
\texttt{k} &  & \\
\texttt{loc} &  & \\
\texttt{w} &  & \\
\addlinespace
\texttt{steps} &  & \\
\texttt{spins} &  & \\
\texttt{hc} &  & \\
\texttt{non\_fac} &  & \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:arg-shape-tb-pdf}Argument definitions for the shape generators. The table lists each argument, its data type, and a description of its role in controlling geometric structure, dimensionality, scaling, curvature, spacing, and other features of the simulated high-dimensional datasets.}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{3cm}l}
\toprule
Argument & Type (positive) & Explanation\\
\midrule
\texttt{n} & integer & Number of points.\\
\texttt{k} & integer & Number of clusters.\\
\texttt{p} & integer & Number of dimensions.\\
\texttt{h} & real value & Height.\\
\texttt{ratio} & real value & Radius tip to radius base ratio.\\
\addlinespace
\texttt{s} & real value & Variance-covariance matrix.\\
\texttt{r} & real value & Radius.\\
\texttt{k\_small} & integer & Number of small spheres.\\
\texttt{r\_vec} & real values & Radius of the big and small spheres.\\
\texttt{spe} & real value & How far the small spheres are placed from each other.\\
\addlinespace
\texttt{w} & real value & Vertical variation\\
\texttt{steps} & integer & Number of steps for the theta parameter.\\
\texttt{spins} & integer & Number of loops of the spiral.\\
\texttt{hc} & real value & Steepness and vertical scaling of the hyperbola.\\
\texttt{non\_fac} & real value & Strength of this sinusoidal effect.\\
\bottomrule
\end{tabular}
\end{table}
